---
title: "Homework 4"
author: "Kendall Pollard"
format:
  pdf:
    output-file: "pollard-k-hwk4-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---


```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```


```{r}
#| include: false
#| eval: true
load("Hw4_workspace.Rdata")
```

Here is the link to my GitHub Repository: 

Here are my answers for Homework 4. I do the coding in a separate `R` script, but here is the cleaned-up version. I run the analysis separately, save the workspace with only the summary stats, figures, and tables that I need, and then load the workspace in the final qmd. My analysis file with answers and code to all the questions is available in the analysis folder. 

\newpage 

\vspace{.2in}
\noindent 1. Remove all SNPs, 800-series plans, and prescription drug only plans (i.e., plans that do not offer Part C benefits). Provide a box and whisker plot showing the distribution of plan counts by county over time. Do you think that the number of plans is sufficient, too few, or too many? <br>

```{r}
#| echo: false
#| label: plancountscounty
#| fig-cap: Question 1 Graph

question1
```

I think 

\newpage 

\vspace{.2in}

\vspace{.2in}
\noindent 2. Provide bar graphs showing the distribution of star ratings in 2010, 2012, and 2015. How has this distribution changed over time? <br>

```{r}
#| echo: false
#| label: starratingsdist
#| fig-cap: Question 2 Graph

question2
```

The distribution has 

\newpage 

\vspace{.2in}
\noindent 3. Plot the average benchmark payment over time from 2010 through 2015. How much has the average benchmark payment risen over the years? <br>

```{r}
#| echo: false
#| label: avbench
#| fig-cap: Question 3 Graph

question3
```

\newpage 

\vspace{.2in}
\noindent 4. Plot the average share of Medicare Advantage (relative to all Medicare eligibles) over time from 2010 through 2015. Has Medicare Advantage increased or decreased in popularity? How does this share correlate with benchmark payments? <br>


```{r}
#| echo: false
#| label: shareofMA
#| fig-cap: Question 4 Graph

question4
```

\newpage 

\vspace{.2in}
\noindent 5. Calculate the running variable underlying the star rating. Provide a table showing the number of plans that are rounded up into a 3-star, 3.5-star, 4-star, 4.5-star, and 5-star rating. <br>
```{r} 
#| echo: false
#| label: runningvariable
#| tbl-cap: "Number of rounded plans"

library(kableExtra)
options(knitr.kable.NA = 0)
knitr::kable(star_rating_counts, 
             col.names=c("Star Ratings", "Number of Plans"),
             format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down"))

```

\newpage 

\vspace{.2in}
\noindent 6. Using the RD estimator with a bandwidth of 0.125, provide an estimate of the effect of receiving a 3-star versus a 2.5 star rating on enrollments. Repeat the exercise to estimate the effects at 3.5 stars, and summarize your results in a table. <br>
```{r}
#| echo: false
#| label: ratings3
#| fig-cap: "3 star vs 2.5 star"

kable(Q6_3, 
      col.names = c("Method", "Coefficient", "Std. Error", "z-value", "Pr(>|z|)", "CI Lower", "CI Upper"),
      format.args = list(big.mark = ","), 
      align = c("l", "c", "c", "c", "c", "c", "c"),
      caption = "RD Estimation Summary",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down"))

```


```{r} 
#| echo: false
#| label: ratings35
#| fig-cap: "3.5 star vs 3 star"

est35
```


\newpage 

\vspace{.2in}
\noindent 7. Repeat your results for bandwidhts of 0.1, 0.12, 0.13, 0.14, and 0.15 (again for 3 and 3.5 stars). Show all of the results in a graph. How sensitive are your findings to the choice of bandwidth? <br>


```{r}
#| echo: false
#| label: diffbandwiths
#| fig-cap: Question 7 Graph

Q7
```

The findings are not sensitive. 

\newpage 

\vspace{.2in}
\noindent 8. Examine (graphically) whether contracts appear to manipulate the running variable. In other words, look at the distribution of the running variable before and after the relevent threshold values. What do you find? <br>
```{r}
#| echo: false
#| label: dens3
#| fig-cap: Question 8 First Graph

dens3
```

```{r}
#| echo: false
#| label: dens35
#| fig-cap: Question 8 Second Graph

dens35
```

\newpage 

\vspace{.2in}
\noindent 9. Similar to question 4, examine whether plans just above the threshold values have different characteristics than contracts just below the threshold values. Use HMO and Part D status as your plan characteristics.<br>



\newpage 

\vspace{.2in}
\noindent 10. Summarize your findings from 5-9. What is the effect of increasing a star rating on enrollments? Briefly explain your results. <br>

